### 2017-02-05 thesis/latex/thesis.tex
Thesis: add updated calculation for step time, bb/ob time.

\subsubsection{ATP binding / unbinding effects}
\subsubsection{Microtubule un/rebinding}
\subsubsection{Conformation change of motor (``priming stroke'')}
A FRET (fluorescent resonance energy transfer) study, which probes the closeness of different labeled domains on a protein, showed that dynein is found in two different major conformations, depending on the nucleotide bound to its AAA1 ATPase site \cite{FRETstatepaper}. When no nucleotide, ATP or ADP is bound, the authors label the protein ``state I.'' When ADP-Pi bound, the motor is said to be in ``state II,'' as shown in Fig \ref{nucleotide-state}. In addition, motors in the presence of the unhydrolyzable ATP analog were found in state II, indicating the transition from state I to II occurs during ATP binding. Similar reasoning shows that the state II to I transition occurs when the protein is ADP bound. This allows the authors to create the state diagram shown in Fig \ref{nucleotide-state-diagram}.\\

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l |}
    \hline
    T & [ATP] \\ \hline
    310.15 K & $1.54*10^{-3}$ M \cite{cellular-atp}\\ \hline
  \end{tabular}
  \caption{Table of physical constants used in simulation.}
  \label{table:parameter-table}
\end{figure}

@@

\begin{align*}
  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
  \tbb &= \frac{\tstep\tbb}{\tstep-\tbb}\\
  \tob &= \tstep-\tbb\\
  &= \tstep - \frac{\tstep\tbb}{\tstep-\tbb}\\
  &= \frac{\left(\tstep-\tbb\right)\tstep\tbb}{\tstep-\tbb}\\
  &= \frac{\tstep\left(\tstep-\tbb\right) - \tstep\tbb}{\tstep-\tbb}\\
  &= \frac{\tstep^2}{\tstep-\tbb}\\
\end{align*}

Thus, by the above equations and using data from (put right paper here), values for $\tbb$ and $\tob$ can be found:

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
    \hline
    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
    100nm/s & 8nm & 0.08 & 3s & 0.08 & 0.002 \\ \hline
  \end{tabular}
  \caption{Table calculating estimates for $\tbb$ and $\tob$.}
  \label{table:parameter-table}
\end{figure}

Todo: get real values for above velocity/steplenght/steptime/processivity based on \textit{in vivo} ATP concentration.\\

>>>>

\subsubsection{ATP binding / unbinding effects}
\subsubsection{Microtubule un/rebinding}
\subsubsection{Domain movement}
Dynein domains have been shown to move in an alternating fashion, with motor domains moving twice the distance of head domains. This indicates an alternate shuffling-type movement.\\

Flesh this out? Make a table of lots of different experiments and what they indicate?\\

\subsubsection{Conformation change of motor (``priming stroke'')}
A FRET (fluorescent resonance energy transfer) study, which probes the closeness of different labeled domains on a protein, showed that dynein is found in two different major conformations, depending on the nucleotide bound to its AAA1 ATPase site \cite{FRETstatepaper}. When no nucleotide, ATP or ADP is bound, the authors label the protein ``state I.'' When ADP-Pi bound, the motor is said to be in ``state II,'' as shown in Fig \ref{nucleotide-state}. In addition, motors in the presence of the unhydrolyzable ATP analog were found in state II, indicating the transition from state I to II occurs during ATP binding. Similar reasoning shows that the state II to I transition occurs when the protein is ADP bound. This allows the authors to create the state diagram shown in Fig \ref{nucleotide-state-diagram}.\\

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l |}
    \hline
    T & [ATP] \\ \hline
    310.15 K & $1mM$\\ \hline
  \end{tabular}
  \caption{Table of physical constants used in simulation.}
  \label{table:parameter-table}
\end{figure}

@@

\begin{align*}
  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
  \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
  \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
  \tob &= \tstep-\tbb\\
  &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
  &= \frac{\tstep^2}{\tstep+\tproc}\\
\end{align*}

Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
    \hline
    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
  \end{tabular}
  \caption{Table calculating estimates for $\tbb$ and $\tob$.}
  \label{table:parameter-table}
\end{figure}
